Low-lying collective excited states in non-integrable system based on stationary phase approximation to the path integral

### 2018-09-14 paper2/draft1-1.tex
draft1.1

>>>>

\begin{figure*}[t]
 \begin{center}
  \includegraphics[width=40mm,angle=-90]{Pbomega_sq.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
	\caption{aa.
}
 \label{fig:N8Pad}
\end{figure*}

\begin{figure*}[t]
 \begin{center}
  \includegraphics[width=40mm,angle=-90]{Pbocc_number.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
	\caption{aa.
}
 \label{fig:N8Pad}
\end{figure*}

\begin{table}
\begin{ruledtabular}
\begin{tabular}{c|cccccc}
   & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
 Exact & $$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $$\\
ASCC+SPA & unbound & $2.31$ & $2.21$ & $2.12$ & $2.04$ & unbound \\ 
\end{tabular}
\end{ruledtabular}
\caption{\label{ex}Excitation energy.}
\end{table}

\begin{figure}[t]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{Pbintra_trans.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
	\caption{aa.
}
 \label{PbPad}
\end{figure}

\begin{figure}[t]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{Pbinter_trans.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
	\caption{aa.
}
 \label{PbPad}
\end{figure}
